---
title: "Example 6: Page Wrap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example 6: Page Wrap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Handle Wide Tables with Page Wrap

Page wrapping will occur 
automatically if the table width exceeds the available page width.  But 
page wrapping can also be controlled using the `page_wrap` parameter on the 
`define()` function.  Below is an example.  Also note the use of the `id_var` 
option to cause the vehicle column to be retained on each wrapped page. 

```{r eval=FALSE, echo=TRUE}  
library(reporter)

# Create temp file name
tmp <- file.path(tempdir(), "example6.txt")

# Prepare data
dat <- mtcars[1:10, ]
dat <- data.frame(vehicle = rownames(dat), dat)

# Define table
tbl <- create_table(dat, show_cols = 1:8) %>% 
  define(vehicle, label = "Vehicle", width = 3, id_var = TRUE, align = "left") %>% 
  define(mpg, label = "Miles per Gallon", width = 1) %>% 
  define(cyl, label = "Cylinders", format = "%.1f") %>% 
  define(disp, label = "Displacement") %>% 
  define(hp, label = "Horsepower", page_wrap = TRUE) %>% 
  define(drat, visible = FALSE) %>% 
  define(wt, label = "Weight") %>% 
  define(qsec, label = "Quarter Mile Time", width = 1.5) 

  
# Create the report
rpt <- create_report(tmp, orientation = "portrait") %>% 
  titles("Listing 2.0", "MTCARS Data Listing with Page Wrap") %>% 
  add_content(tbl, align = "left") %>% 
  page_footer(right = "Page [pg] of [tpg]")

# Write the report
write_report(rpt)

# Send report to console for viewing
writeLines(readLines(tmp, encoding = "UTF-8"))

#                                  Listing 2.0
#                       MTCARS Data Listing with Page Wrap
# 
#                                         Miles per
# Vehicle                                    Gallon Cylinders Displacement
# ¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯
# Mazda RX4                                      21       6.0          160
# Mazda RX4 Wag                                  21       6.0          160
# Datsun 710                                   22.8       4.0          108
# Hornet 4 Drive                               21.4       6.0          258
# Hornet Sportabout                            18.7       8.0          360
# Valiant                                      18.1       6.0          225
# Duster 360                                   14.3       8.0          360
# Merc 240D                                    24.4       4.0        146.7
# Merc 230                                     22.8       4.0        140.8
# Merc 280                                     19.2       6.0        167.6
# 
# ...
# 
#                                                                    Page 1 of 2
#                                  Listing 2.0
#                       MTCARS Data Listing with Page Wrap
# 
# Vehicle                              Horsepower Weight  Quarter Mile Time
# ¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯
# Mazda RX4                                   110   2.62              16.46
# Mazda RX4 Wag                               110  2.875              17.02
# Datsun 710                                   93   2.32              18.61
# Hornet 4 Drive                              110  3.215              19.44
# Hornet Sportabout                           175   3.44              17.02
# Valiant                                     105   3.46              20.22
# Duster 360                                  245   3.57              15.84
# Merc 240D                                    62   3.19                 20
# Merc 230                                     95   3.15               22.9
# Merc 280                                    123   3.44               18.3
# 
# ...
# 
#                                                                    Page 2 of 2

```

Next: [Example 7: Page By](reporter-pageby.html)
