---
title: "Example 7: Page By"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example 7: Page By}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Create a Table with a By-Group

A page by variable will split the report into pages by a variable, and
label each page according the variable value.  The page by can be assigned to
the report, to a table, or to a plot.  The page by label will appear between
the titles and the content body.  It can be aligned left, right, or center.
The data should be sorted by the page by variable prior to reporting.

```{r eval=FALSE, echo=TRUE}  
# Create temp file name
tmp <- file.path(tempdir(), "example7.txt")

# Prepare data
dat <- mtcars[order(mtcars$cyl), ]
dat <- data.frame(vehicle = rownames(dat), dat)

# Define table
tbl <- create_table(dat, show_cols = 1:8) %>% 
  page_by(cyl, label="Cylinders: ") 

# Create the report
rpt <- create_report(tmp, orientation = "portrait") %>% 
  titles("Listing 3.0", "MTCARS Data Listing with Page By") %>% 

  add_content(tbl) 


# Write the report
write_report(rpt)

# Send report to console for viewing
writeLines(readLines(tmp, encoding = "UTF-8"))

#                                 Listing 3.0
#                       MTCARS Data Listing with Page By
#
#       Cylinders: 4
#
#       vehicle                mpg cyl   disp   hp  drat     wt   qsec
#       ¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯
#       Datsun 710            22.8   4    108   93  3.85   2.32  18.61
#       Merc 240D             24.4   4  146.7   62  3.69   3.19     20
#       Merc 230              22.8   4  140.8   95  3.92   3.15   22.9
#       Fiat 128              32.4   4   78.7   66  4.08    2.2  19.47
#       Honda Civic           30.4   4   75.7   52  4.93  1.615  18.52
#       Toyota Corolla        33.9   4   71.1   65  4.22  1.835   19.9
#       Toyota Corona         21.5   4  120.1   97   3.7  2.465  20.01
#       Fiat X1-9             27.3   4     79   66  4.08  1.935   18.9
#       Porsche 914-2           26   4  120.3   91  4.43   2.14   16.7
#       Lotus Europa          30.4   4   95.1  113  3.77  1.513   16.9
#       Volvo 142E            21.4   4    121  109  4.11   2.78   18.6
#
# ...
#
#                                 Listing 3.0
#                       MTCARS Data Listing with Page By
#
#       Cylinders: 6
#
#       vehicle                mpg cyl   disp   hp  drat     wt   qsec
#       ¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯
#       Mazda RX4               21   6    160  110   3.9   2.62  16.46
#       Mazda RX4 Wag           21   6    160  110   3.9  2.875  17.02
#       Hornet 4 Drive        21.4   6    258  110  3.08  3.215  19.44
#       Valiant               18.1   6    225  105  2.76   3.46  20.22
#       Merc 280              19.2   6  167.6  123  3.92   3.44   18.3
#       Merc 280C             17.8   6  167.6  123  3.92   3.44   18.9
#       Ferrari Dino          19.7   6    145  175  3.62   2.77   15.5
#
# ...
#
#                                 Listing 3.0
#                       MTCARS Data Listing with Page By
#
#       Cylinders: 8
#
#       vehicle                mpg cyl   disp   hp  drat     wt   qsec
#       ¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯¯
#       Hornet Sportabout     18.7   8    360  175  3.15   3.44  17.02
#       Duster 360            14.3   8    360  245  3.21   3.57  15.84
#       Merc 450SE            16.4   8  275.8  180  3.07   4.07   17.4
#       Merc 450SL            17.3   8  275.8  180  3.07   3.73   17.6
#       Merc 450SLC           15.2   8  275.8  180  3.07   3.78     18
#       Cadillac Fleetwood    10.4   8    472  205  2.93   5.25  17.98
#       Lincoln Continental   10.4   8    460  215     3  5.424  17.82
#       Chrysler Imperial     14.7   8    440  230  3.23  5.345  17.42
#       Dodge Challenger      15.5   8    318  150  2.76   3.52  16.87
#       AMC Javelin           15.2   8    304  150  3.15  3.435   17.3
#       Camaro Z28            13.3   8    350  245  3.73   3.84  15.41
#       Pontiac Firebird      19.2   8    400  175  3.08  3.845  17.05
#       Ford Pantera L        15.8   8    351  264  4.22   3.17   14.5
#       Maserati Bora           15   8    301  335  3.54   3.57   14.6
#

```
